---
title: "R Notebook"
output: html_notebook
---

```{r}
library(readr)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(tidyr)
library(gplots)
library(lmerTest)
library(emmeans)
library(cowplot)
```

```{r}
Response_Time <- read_csv("../Data/MeasurementsFiltered/Response_ReactionTime.csv")
Accuracy <- read_csv("../Data/MeasurementsFiltered/Accuracy.csv")

# 只取PE中第二次的時間
PE_Second <- Response_Time[!(Response_Time$Status %in% c("PEM", "PECon", "PECre")), ]

# 只有PE的所有狀態
PE_filtered_data <- Response_Time %>% filter(grepl("PE", Condition))

print(Response_Time)
print(Accuracy)
print(PE_Second)
print(PE_filtered_data)
```

# Calculative_Response_Statistic
```{r}
# Assuming Calculative_Response_Statistic has columns for each status and counts
unique_ids <- unique(Response_Time$ParticipantId)
statuses <- unique(Response_Time$Status)
columns <- c("ParticipantId", sapply(statuses, function(x) paste0(x, c("StrictCount", "TolerantCount", "StrictRate", "TolerantRate"))))

# Initialize the data frame
Calculative_Response_Statistic <- as.data.frame(matrix(0, nrow = length(unique_ids), ncol = length(columns)))
colnames(Calculative_Response_Statistic) <- columns
Calculative_Response_Statistic$ParticipantId <- unique_ids


# Ensure the required columns exist
for (status in statuses) {
  Calculative_Response_Statistic[paste0(status, "StrictCount")] <- 0
  Calculative_Response_Statistic[paste0(status, "TolerantCount")] <- 0
}

for (i in seq(1, nrow(Response_Time))) {
  current_data <- Response_Time[i, ]
  current_accuracy <- Accuracy[Accuracy$PictureName == current_data$PictureName, "Answer"]
  
  if (length(current_accuracy) > 0) {
    status <- as.character(current_data$Status)
    id <- as.character(current_data$ParticipantId)
    response <- as.numeric(current_data$Response) # Ensure response is numeric
    
    # Ensure the participant ID exists in Calculative_Response_Statistic
    if (id %in% Calculative_Response_Statistic$ParticipantId) {
      # Update StrictCount and TolerantCount
      if (response == current_accuracy) {
        Calculative_Response_Statistic[Calculative_Response_Statistic$ParticipantId == id, paste0(status, "StrictCount")] <- 
          Calculative_Response_Statistic[Calculative_Response_Statistic$ParticipantId == id, paste0(status, "StrictCount")] + 1
        
        Calculative_Response_Statistic[Calculative_Response_Statistic$ParticipantId == id, paste0(status, "TolerantCount")] <- 
          Calculative_Response_Statistic[Calculative_Response_Statistic$ParticipantId == id, paste0(status, "TolerantCount")] + 1
      } else if (any(abs(response - current_accuracy) == 1)) {
        Calculative_Response_Statistic[Calculative_Response_Statistic$ParticipantId == id, paste0(status, "TolerantCount")] <- 
          Calculative_Response_Statistic[Calculative_Response_Statistic$ParticipantId == id, paste0(status, "TolerantCount")] + 1
      }
      
      # Calculate and update StrictRate and TolerantRate
      strict_count <- Calculative_Response_Statistic[Calculative_Response_Statistic$ParticipantId == id, paste0(status, "StrictCount")]
      tolerant_count <- Calculative_Response_Statistic[Calculative_Response_Statistic$ParticipantId == id, paste0(status, "TolerantCount")]
      
      Calculative_Response_Statistic[Calculative_Response_Statistic$ParticipantId == id, paste0(status, "StrictRate")] <- round(strict_count / 10, 2)
      Calculative_Response_Statistic[Calculative_Response_Statistic$ParticipantId == id, paste0(status, "TolerantRate")] <- round(tolerant_count / 10, 2)
    } else {
      print(paste("ID", id, "not found in Calculative_Response_Statistic"))
    }
  }
}

print(Calculative_Response_Statistic)

```


## 整理 Calculative_Response_Statistic

```{r}
Calculative_Response_Statistic_long <- gather(Calculative_Response_Statistic, Type, Value, -ParticipantId)

Calculative_Response_Statistic_long$Condition <- case_when(
  grepl("CCTCre", Calculative_Response_Statistic_long$Type) ~ "CCTCre",
  grepl("CCTCon", Calculative_Response_Statistic_long$Type) ~ "CCTCon",
  grepl("CCTM", Calculative_Response_Statistic_long$Type) ~ "CCTM",
  grepl("PECre", Calculative_Response_Statistic_long$Type) ~ "PECre",
  grepl("PECon", Calculative_Response_Statistic_long$Type) ~ "PECon",
  grepl("PEM", Calculative_Response_Statistic_long$Type) ~ "PEM",
  grepl("Control", Calculative_Response_Statistic_long$Type) ~ "Control",
  TRUE ~ NA_character_
)

Calculative_Response_Statistic_long$Placement <- case_when(
  grepl("CCTCre|CCTCon|CCTM", Calculative_Response_Statistic_long$Type) ~ "Concurrent",
  grepl("PECre|PECon|PEM", Calculative_Response_Statistic_long$Type) ~ "Post-Exposure",
  grepl("Control", Calculative_Response_Statistic_long$Type) ~ "Control",
  TRUE ~ NA_character_
)

Calculative_Response_Statistic_long$LabelType <- case_when(
  grepl("CCTCre|PECre", Calculative_Response_Statistic_long$Type) ~ "Credibility",
  grepl("CCTCon|PECon", Calculative_Response_Statistic_long$Type) ~ "Contextual",
  grepl("CCTM|PEM", Calculative_Response_Statistic_long$Type) ~ "Mixed",
  grepl("Control", Calculative_Response_Statistic_long$Type) ~ "Control",
  TRUE ~ NA_character_
)

print(Calculative_Response_Statistic_long)

Exclude_Control_Response <- Calculative_Response_Statistic_long[!(Calculative_Response_Statistic_long$Condition %in% "Control"), ]
print(Exclude_Control_Response)

# Strict without Control
Strict_Without_data <- Exclude_Control_Response[grepl("StrictRate", Exclude_Control_Response$Type) & !grepl("Post-Exposure", Exclude_Control_Response$Type), ]
print(Strict_Without_data)

# Strict with Control
Strict_With_data <- Calculative_Response_Statistic_long[grepl("StrictRate", Calculative_Response_Statistic_long$Type) & !grepl("Post-Exposure", Calculative_Response_Statistic_long$Type), ]
print(Strict_With_data)

# Tolerant without Control
Tolerant_Without_data <- Exclude_Control_Response[grepl("TolerantRate", Exclude_Control_Response$Type) & !grepl("Post-Exposure", Exclude_Control_Response$Type), ]
print(Tolerant_Without_data)

# Tolerant with Control
Tolerant_With_data <- Calculative_Response_Statistic_long[grepl("TolerantRate", Calculative_Response_Statistic_long$Type) & !grepl("Post-Exposure", Calculative_Response_Statistic_long$Type), ]
print(Tolerant_With_data)

```

## Descriptive Statistics

```{r}
summary(Strict_With_data)
cat("Standard derivation of Strict Accuracy: ", sd(Strict_With_data$Value))
cat("\n")

summary(Tolerant_With_data)
cat("Standard derivation of Tolerant Accuracy: ", sd(Tolerant_With_data$Value
))
```


## PlotMeans: StrictRate, TolerantRate
- Strict Rate

```{r}
# Reorder the levels of the "Condition" factor so that "Control" comes first
Strict_With_data <- Strict_With_data %>%
  mutate(Condition = factor(Condition, levels = c("Control", "CCTCon", "CCTCre", "CCTM", "PECon", "PECre", "PEM")))


saall_stats <- Strict_With_data %>%
  group_by(Condition, Placement) %>%
  summarize(
    mean_sa = round(mean(Value*100), 2),
    sd_sa = round(sd(Value*100), 2),
    n = n(),  # Sample size for each group
    se_sa = sd_sa / sqrt(n),  # Standard Error
    ci_sa = qt(0.975, df = n - 1) * se_sa  # 95% Confidence Interval
  )
print(saall_stats)

# Define custom colors for each combination of Placement and LabelType
custom_colors <- c(
  "Control" = "#fa75a2",
  "CCTCon" = "#a6cee3",  # light blue
  "CCTCre" = "#1f78b4",  # medium blue
  "CCTM" = "#2e4194",  # dark blue
  "PECon" = "#b2df8a",  # light green
  "PECre" = "#33a02c",  # medium green
  "PEM" = "#006400"  # dark green
)

# Plot the boxplot with error bars
saall <- ggplot(data = saall_stats, aes(x = Condition, y = mean_sa, fill = Condition)) + 
  scale_fill_manual(values = custom_colors) +
  geom_col(width = 0.6) +
  geom_errorbar(data = saall_stats, 
                aes(x = Condition, ymin = mean_sa - ci_sa, ymax = mean_sa + ci_sa), width = 0.3, color = "black") +
  labs(x = "Condition", y = "Accuracy (%)") +
  ylim(0,100) +
  theme_minimal() +
  theme(
    plot.margin = unit(c(0.2, 0.2, 0.2, 0.2), "inches"),
    axis.title.x = element_text(face = "bold", size = 13, margin = margin(t = 15)),
    axis.title.y = element_text(face = "bold", size = 13, margin = margin(r = 15)),
    axis.text = element_text(size = 11),
    panel.grid = element_blank(),  # 取消所有格線
    axis.line = element_line(color = "black", size = 0.5),  # 顯示 y 軸和 x 軸線
    axis.ticks = element_line(color = "black", size = 0.5),  # 顯示刻度線
    axis.ticks.length = unit(0.2, "cm")  # 設定刻度線的長度
  ) +
  guides(fill = FALSE)  # Remove the legend for the fill

saall

# ggsave(saall,
#       filename = "/Users/edwina/Desktop/ResearchOfEdwina/Codes/Quantitative/RPlots/Accuracy/Strict/Strict Accuracy vs All Conditions.pdf",
#        device = "pdf" )
```

- Tolerant Rate

```{r}
# Reorder the levels of the "Condition" factor so that "Control" comes first
Tolerant_With_data <- Tolerant_With_data %>%
  mutate(Condition = factor(Condition, levels = c("Control", "CCTCon", "CCTCre", "CCTM", "PECon", "PECre", "PEM")))

taall_stats <- Tolerant_With_data %>%
  group_by(Condition, Placement) %>%
  summarize(
    mean_ta = round(mean(Value*100), 2),
    sd_ta = round(sd(Value*100), 2),
    n = n(),  # Sample size for each group
    se_ta = sd_ta / sqrt(n) ,  # Standard Error
    ci_ta = qt(0.975, df = n - 1) * se_ta  # 95% Confidence Interval
  )
print(taall_stats)

# Define custom colors for each combination of Placement and LabelType
custom_colors <- c(
  "Control" = "#fa75a2",
  "CCTCon" = "#a6cee3",  # light blue
  "CCTCre" = "#1f78b4",  # medium blue
  "CCTM" = "#2e4194",  # dark blue
  "PECon" = "#b2df8a",  # light green
  "PECre" = "#33a02c",  # medium green
  "PEM" = "#006400"  # dark green
)

# Plot the boxplot with error bars
taall <- ggplot(data = taall_stats, aes(x = Condition, y = mean_ta, fill = Condition)) + 
  scale_fill_manual(values = custom_colors) + 
  geom_col(width = 0.6) +
  geom_errorbar(data = taall_stats, 
                aes(x = Condition, ymin = mean_ta - ci_ta, ymax = mean_ta + ci_ta), width = 0.3, color = "black") +
  labs(x = "Condition", y = "Accuracy (%)") +
  ylim(0,100) +
  theme_minimal() +
  theme(
    plot.margin = unit(c(0.2, 0.2, 0.2, 0.2), "inches"),
    axis.title.x = element_text(face = "bold", size = 13, margin = margin(t = 15)),
    axis.title.y = element_text(face = "bold", size = 13, margin = margin(r = 15)),
    axis.text = element_text(size = 11),
    panel.grid = element_blank(),  # 取消所有格線
    axis.line = element_line(color = "black", size = 0.5),  # 顯示 y 軸和 x 軸線
    axis.ticks = element_line(color = "black", size = 0.5),  # 顯示刻度線
    axis.ticks.length = unit(0.2, "cm")  # 設定刻度線的長度
  ) +
  guides(fill = FALSE)  # Remove the legend for the fill

taall
# ggsave(taall,
#       filename = "/Users/edwina/Desktop/ResearchOfEdwina/Codes/Quantitative/RPlots/Accuracy/Tolerant/Tolerant Accuracy vs All Conditions.pdf",
#        device = "pdf" )
```


## Two-Way ANOVA (Strict without Control)

```{r}
Strict_TwoWay_MEM <- lmer(Value ~ Placement * LabelType + (1|ParticipantId), data = Strict_Without_data)
anova(Strict_TwoWay_MEM)

# Post-hoc
Strict_TwoWay_pairwise <- pairs(emmeans(Strict_TwoWay_MEM, ~ Placement * LabelType))
print(Strict_TwoWay_pairwise)
Strict_TwoWay_summary_pairwise <- summary(Strict_TwoWay_pairwise)
# str(summary_pairwise)
#print(summary_pairwise$p.value)

Strict_TwoWay_significant_contrasts <- Strict_TwoWay_summary_pairwise$contrast[Strict_TwoWay_summary_pairwise$p.value <= 0.05]

Strict_TwoWay_significant_df <- Strict_TwoWay_summary_pairwise$df[Strict_TwoWay_summary_pairwise$p.value <= 0.05]

Strict_TwoWay_significant_tratio <- Strict_TwoWay_summary_pairwise$t.ratio[Strict_TwoWay_summary_pairwise$p.value <= 0.05]

Strict_TwoWay_significant_p_values <- Strict_TwoWay_summary_pairwise$p.value[Strict_TwoWay_summary_pairwise$p.value <= 0.05]
Strict_TwoWay_significant_p_values <- round(Strict_TwoWay_significant_p_values, 3)

Strict_TwoWay_significant_results <- data.frame(contrast = Strict_TwoWay_significant_contrasts, df = Strict_TwoWay_significant_df, t.ratio = Strict_TwoWay_significant_tratio, p.value = Strict_TwoWay_significant_p_values)

print(Strict_TwoWay_significant_results)
```

## Interaction of Label Type and Placement

```{r}
pairs(emmeans(Strict_TwoWay_MEM, "LabelType"))
pairs(emmeans(Strict_TwoWay_MEM, "Placement"))

salabel_stats <- Strict_Without_data %>%
  group_by(LabelType) %>%
  summarize(
    mean_salabel = round(mean(Value*100), 2),
    sd_salabel = round(sd(Value*100), 2),
    n = n(),  # Sample size for each group
    se_salabel = sd_salabel / sqrt(n) ,  # Standard Error
    ci_salabel = qt(0.975, df = n - 1) * se_salabel  # 95% Confidence Interval
  )
print(salabel_stats)

# Plot the boxplot with error bars
sa_lt <- ggplot(data = salabel_stats, aes(x = LabelType, y = mean_salabel, fill = LabelType)) + 
  scale_fill_brewer(palette="Greys") +
  geom_col(width = 0.6) +
  geom_errorbar(data = salabel_stats, 
                aes(x = LabelType, ymin = mean_salabel - ci_salabel, ymax =  mean_salabel + ci_salabel), width = 0.2, color = "black") +
  labs(x = "(A) Label Type", y = "Accuracy (%)") +
  ylim(0, 100) +
  theme_minimal() +
  theme(
    axis.title.x = element_text(face = "bold", size = 13, margin = margin(t = 15)),
    axis.title.y = element_text(face = "bold", size = 13, margin = margin(r = 15)),
    axis.text = element_text(size = 11),
    axis.text.x = element_text(angle=45, vjust=1, hjust=1),
    panel.grid = element_blank(),  # 取消所有格線
    axis.line = element_line(color = "black", size = 0.5),  # 顯示 y 軸和 x 軸線
    axis.ticks = element_line(color = "black", size = 0.5),  # 顯示刻度線
    axis.ticks.length = unit(0.2, "cm")  # 設定刻度線的長度
  ) +
  guides(fill = FALSE)  # Remove the legend for the fill

saplacement_stats <- Strict_Without_data %>%
  group_by(Placement) %>%
  summarize(
    mean_saplacement = round(mean(Value*100), 2),
    sd_saplacement = round(sd(Value*100), 2),
    n = n(),  # Sample size for each group
    se_saplacement = sd_saplacement / sqrt(n) ,  # Standard Error
    ci_saplacement = qt(0.975, df = n - 1) * se_saplacement  # 95% Confidence Interval
  )
print(saplacement_stats)

# Plot the boxplot with error bars
sa_pt <- ggplot(data = saplacement_stats, aes(x = Placement, y = mean_saplacement, fill = Placement)) + 
  scale_fill_manual(values = c("Concurrent" = "#1f78b4",
                               "Post-Exposure" = "#33a02c")) + 
  geom_col(width = 0.4) +
  geom_errorbar(data = saplacement_stats, 
                aes(x = Placement, ymin = mean_saplacement - ci_saplacement, ymax =  mean_saplacement + ci_saplacement), width = 0.2, color = "black") +
  labs(x = "(B) Placement") +
  ylim(0, 100) +
  theme_minimal() +
  theme(
    axis.title.x = element_text(face = "bold", size = 13, margin = margin(t = 15)),
    axis.title.y = element_blank(),  # 取消顯示 y 軸名稱
    axis.text = element_text(size = 11),
    axis.text.x = element_text(angle=45, vjust=1, hjust=1),
    panel.grid = element_blank(),  # 取消所有格線
    axis.line = element_line(color = "black", size = 0.5),  # 顯示 y 軸和 x 軸線
    axis.ticks = element_line(color = "black", size = 0.5),  # 顯示刻度線
    axis.ticks.length = unit(0.2, "cm")  # 設定刻度線的長度
  ) +
  guides(fill = FALSE)  # Remove the legend for the fill

sa_fig <- ggarrange(
  sa_lt, sa_pt,
  ncol = 2, nrow = 1,
  align = "h"  # 垂直對齊
)
sa_fig + theme(plot.margin = unit(c(0.3, 0.2, 0.1, 0.2), "inches"))

# ggsave(sa_fig, 
#       filename = "/Users/edwina/Desktop/ResearchOfEdwina/Codes/Quantitative/RPlots/Accuracy/Strict/Strict Accuracy of Lable Type and Placement.pdf",
#        device = "pdf" )
```


## Two-Way ANOVA (Tolerant without Control)

```{r}
Tolerant_TwoWay_MEM <- lmer(Value ~ Placement * LabelType + (1|ParticipantId), data = Tolerant_Without_data)
Tolerant_TwoWay_LabelType <- lmer(Value ~ LabelType + (1|ParticipantId), data = Tolerant_Without_data)
Tolerant_TwoWay_Placement <- lmer(Value ~ Placement + (1|ParticipantId), data = Tolerant_Without_data)

anova(Tolerant_TwoWay_MEM)

# Post-hoc
Tolerant_TwoWay_pairwise <- pairs(emmeans(Tolerant_TwoWay_MEM, ~ Placement * LabelType))
print(Tolerant_TwoWay_pairwise)
Tolerant_TwoWay_summary_pairwise <- summary(Tolerant_TwoWay_pairwise)
# str(summary_pairwise)
#print(summary_pairwise$p.value)

Tolerant_TwoWay_significant_contrasts <- Tolerant_TwoWay_summary_pairwise$contrast[Tolerant_TwoWay_summary_pairwise$p.value <= 0.05]

Tolerant_TwoWay_significant_df <- Tolerant_TwoWay_summary_pairwise$df[Tolerant_TwoWay_summary_pairwise$p.value <= 0.05]

Tolerant_TwoWay_significant_tratio <- Tolerant_TwoWay_summary_pairwise$t.ratio[Tolerant_TwoWay_summary_pairwise$p.value <= 0.05]

Tolerant_TwoWay_significant_p_values <- Tolerant_TwoWay_summary_pairwise$p.value[Tolerant_TwoWay_summary_pairwise$p.value <= 0.05]
Tolerant_TwoWay_significant_p_values <- round(Tolerant_TwoWay_significant_p_values, 3)

Tolerant_TwoWay_significant_results <- data.frame(contrast = Tolerant_TwoWay_significant_contrasts, df = Tolerant_TwoWay_significant_df, t.ratio = Tolerant_TwoWay_significant_tratio, p.value = Tolerant_TwoWay_significant_p_values)

print(Tolerant_TwoWay_significant_results)
```

## Interaction of Label Type and Placement

```{r}
pairs(emmeans(Tolerant_TwoWay_MEM, "LabelType"))
pairs(emmeans(Tolerant_TwoWay_MEM, "Placement"))

talabel_stats <- Tolerant_Without_data %>%
  group_by(LabelType) %>%
  summarize(
    mean_talabel = round(mean(Value*100), 2),
    sd_talabel = round(sd(Value*100), 2),
    n = n(),  # Sample size for each group
    se_talabel = sd_talabel / sqrt(n) ,  # Standard Error
    ci_talabel = qt(0.975, df = n - 1) * se_talabel  # 95% Confidence Interval
  )
print(talabel_stats)

# Plot the boxplot with error bars
ta_lt <- ggplot(data = talabel_stats, aes(x = LabelType, y = mean_talabel, fill = LabelType)) + 
  scale_fill_brewer(palette="Greys") +
  geom_col(width = 0.6) +
  geom_errorbar(aes(x = LabelType, ymin = mean_talabel - ci_talabel, ymax =  mean_talabel + ci_talabel), width = 0.2, color = "black") +
  labs(x = "(A) Label Type", y = "Accuracy (%)") +
  ylim(0, 100) +
  theme_minimal() +
  theme(
    axis.title.x = element_text(face = "bold", size = 13, margin = margin(t = 15)),
    axis.title.y = element_text(face = "bold", size = 13, margin = margin(r = 15)),
    axis.text = element_text(size = 11),
    axis.text.x = element_text(angle=45, vjust=1, hjust=1),
    panel.grid = element_blank(),  # 取消所有格線
    axis.line = element_line(color = "black", size = 0.5),  # 顯示 y 軸和 x 軸線
    axis.ticks = element_line(color = "black", size = 0.5),  # 顯示刻度線
    axis.ticks.length = unit(0.2, "cm")  # 設定刻度線的長度
  ) +
  guides(fill = FALSE)  # Remove the legend for the fill

taplacement_stats <- Tolerant_Without_data %>%
  group_by(Placement) %>%
  summarize(
    mean_taplacemnt = round(mean(Value*100), 2),
    sd_taplacemnt = round(sd(Value*100), 2),
    n = n(),  # Sample size for each group
    se_taplacemnt = sd_taplacemnt / sqrt(n) ,  # Standard Error
    ci_taplacemnt = qt(0.975, df = n - 1) * se_taplacemnt  # 95% Confidence Interval
  )
print(taplacement_stats)

# Plot the boxplot with error bars
ta_pt <- ggplot(data = taplacement_stats, aes(x = Placement, y = mean_taplacemnt, fill = Placement)) + 
  scale_fill_manual(values = c("Concurrent" = "#1f78b4",
                               "Post-Exposure" = "#33a02c")) +
  geom_col(width = 0.4) +
  geom_errorbar(aes(x = Placement, ymin = mean_taplacemnt - ci_taplacemnt, ymax =  mean_taplacemnt + ci_taplacemnt), width = 0.2, color = "black") +
  labs(x = "(B) Placement") +
  ylim(0, 100) +
  theme_minimal() +
  theme(
    axis.title.x = element_text(face = "bold", size = 13, margin = margin(t = 15)),
    axis.title.y = element_blank(),  # 取消顯示 y 軸名稱
    axis.text = element_text(size = 11),
    axis.text.x = element_text(angle=45, vjust=1, hjust=1),
    panel.grid = element_blank(),  # 取消所有格線
    axis.line = element_line(color = "black", size = 0.5),  # 顯示 y 軸和 x 軸線
    axis.ticks = element_line(color = "black", size = 0.5),  # 顯示刻度線
    axis.ticks.length = unit(0.2, "cm")  # 設定刻度線的長度
  ) +
  guides(fill = FALSE)  # Remove the legend for the fill

ta_fig <- ggarrange(
  ta_lt, ta_pt,
  ncol = 2, nrow = 1,
  align = "h"  # 垂直對齊
)
ta_fig + theme(plot.margin = unit(c(0.3, 0.2, 0.1, 0.2), "inches"))

# ggsave(ta_fig, 
#       filename = "/Users/edwina/Desktop/ResearchOfEdwina/Codes/Quantitative/RPlots/Accuracy/Tolerant/Tolerant Accuracy of Lable Type and Placement.pdf",
#        device = "pdf" )
```

## One-Way ANOVA (Strict with Control)

```{r}
Strict_OneWay_MEM <- lmer(Value ~ Condition + (1|ParticipantId), data = Strict_With_data)
anova(Strict_OneWay_MEM)

# Post-Hoc
Strict_OneWay_pairwise <- pairs(emmeans(Strict_OneWay_MEM, ~ Condition))
print(Strict_OneWay_pairwise)

Strict_OneWay_summary_pairwise <- summary(Strict_OneWay_pairwise)
# str(summary_pairwise)
# print(summary_pairwise$p.value)

Strict_OneWay_significant_contrasts <- Strict_OneWay_summary_pairwise$contrast[Strict_OneWay_summary_pairwise$p.value <= 0.05]

Strict_OneWay_significant_df <- Strict_OneWay_summary_pairwise$df[Strict_OneWay_summary_pairwise$p.value <= 0.05]

Strict_OneWay_significant_tratio <- Strict_OneWay_summary_pairwise$t.ratio[Strict_OneWay_summary_pairwise$p.value <= 0.05]

Strict_OneWay_significant_p_values <- Strict_OneWay_summary_pairwise$p.value[Strict_OneWay_summary_pairwise$p.value <= 0.05]
Strict_OneWay_significant_p_values <- round(Strict_OneWay_significant_p_values, 3)

Strict_OneWay_significant_results <- data.frame(contrast = Strict_OneWay_significant_contrasts, df = Strict_OneWay_significant_df, t.ratio = Strict_OneWay_significant_tratio, p.value = Strict_OneWay_significant_p_values)

print(Strict_OneWay_significant_results)
```

## One-Way ANOVA (Tolerant with Control)

```{r}
Tolerant_OneWay_MEM <- lmer(Value ~ Condition + (1|ParticipantId), data = Tolerant_With_data)
anova(Tolerant_OneWay_MEM)

# Post-Hoc
Tolerant_OneWay_pairwise <- pairs(emmeans(Tolerant_OneWay_MEM, ~ Condition))
print(Tolerant_OneWay_pairwise)

Tolerant_OneWay_summary_pairwise <- summary(Tolerant_OneWay_pairwise)
# str(summary_pairwise)
# print(summary_pairwise$p.value)

Tolerant_OneWay_significant_contrasts <- Tolerant_OneWay_summary_pairwise$contrast[Tolerant_OneWay_summary_pairwise$p.value <= 0.05]

Tolerant_OneWay_significant_df <- Tolerant_OneWay_summary_pairwise$df[Tolerant_OneWay_summary_pairwise$p.value <= 0.05]

Tolerant_OneWay_significant_tratio <- Tolerant_OneWay_summary_pairwise$t.ratio[Tolerant_OneWay_summary_pairwise$p.value <= 0.05]

Tolerant_OneWay_significant_p_values <- Tolerant_OneWay_summary_pairwise$p.value[Tolerant_OneWay_summary_pairwise$p.value <= 0.05]
Tolerant_OneWay_significant_p_values <- round(Tolerant_OneWay_significant_p_values, 3)

Tolerant_OneWay_significant_results <- data.frame(contrast = Tolerant_OneWay_significant_contrasts, df = Tolerant_OneWay_significant_df, t.ratio = Tolerant_OneWay_significant_tratio, p.value = Tolerant_OneWay_significant_p_values)
print(Tolerant_OneWay_significant_results)
```

# PE組內比較

```{r}
# Strict 
PE_Strict <- Exclude_Control_Response[grepl("StrictRate", Exclude_Control_Response$Type) & grepl("Post-Exposure", Exclude_Control_Response$Placement), ]


print(PE_Strict)

# Tolerant 
PE_Tolerant <- Exclude_Control_Response[grepl("TolerantRate", Exclude_Control_Response$Type) & grepl("Post-Exposure", Exclude_Control_Response$Placement), ]

print(PE_Tolerant)
```

## PE Strict One-Way

```{r}
PE_Strict_OneWay_MEM <- lmer(Value ~ Type + (1|ParticipantId), data = PE_Strict)
anova(PE_Strict_OneWay_MEM)


# Post-Hoc
PE_Strict_One_Way_pairwise <- pairs(emmeans(PE_Strict_OneWay_MEM, ~ Type))
print(PE_Strict_One_Way_pairwise)

PE_Strict_One_Way_summary_pairwise <- summary(PE_Strict_One_Way_pairwise)
# str(summary_pairwise)
# print(summary_pairwise$p.value)

PE_Strict_One_Way_significant_contrasts <- PE_Strict_One_Way_summary_pairwise$contrast[PE_Strict_One_Way_summary_pairwise$p.value <= 0.05]

PE_Strict_One_Way_significant_df <- PE_Strict_One_Way_summary_pairwise$df[PE_Strict_One_Way_summary_pairwise$p.value <= 0.05]

PE_Strict_One_Way_significant_tratio <- PE_Strict_One_Way_summary_pairwise$t.ratio[PE_Strict_One_Way_summary_pairwise$p.value <= 0.05]

PE_Strict_One_Way_significant_p_values <- PE_Strict_One_Way_summary_pairwise$p.value[PE_Strict_One_Way_summary_pairwise$p.value <= 0.05]
PE_Strict_One_Way_significant_p_values <- round(PE_Strict_One_Way_significant_p_values, 3)

PE_Strict_One_Way_significant_results <- data.frame(contrast = PE_Strict_One_Way_significant_contrasts, df = PE_Strict_One_Way_significant_df, t.ratio = PE_Strict_One_Way_significant_tratio, p.value = PE_Strict_One_Way_significant_p_values)

print(PE_Strict_One_Way_significant_results)
```

```{r}
unique(PE_Strict$Type)
PE_Strict <- PE_Strict %>%
  mutate(
    Type = case_when(
      Type == "PECreStrictRate" ~ "1st",
      Type == "PECre_Post-ExposureStrictRate" ~ "2nd",
      Type == "PEConStrictRate" ~ "1st",
      Type == "PECon_Post-ExposureStrictRate" ~ "2nd",
      Type == "PEMStrictRate" ~ "1st",
      Type == "PEM_Post-ExposureStrictRate" ~ "2nd",
      TRUE ~ Type  # Keep the original value for any unmatched cases
    )
  )

pe_saall_stats <- PE_Strict %>%
  group_by(Type, Condition) %>%
  summarize(
    pe_mean_sa = round(mean(Value*100), 2),
    pe_sd_sa = round(sd(Value*100), 2),
    n = n(),
    pe_se_sa = pe_sd_sa / sqrt(n) ,  # Standard Error
    pe_ci_sa = qt(0.975, df = n - 1) * pe_se_sa  # 95% Confidence Interval
  )
print(pe_saall_stats)

# 繪製圖形
sapecom_plot <- ggplot(data = pe_saall_stats, aes(x = Condition, y = pe_mean_sa, fill = Type)) + 
  scale_fill_brewer(palette="Reds") +
  geom_bar(stat="identity", position=position_dodge(width = 0.9), width = 0.9) +
  geom_errorbar(aes(ymin = pe_mean_sa - pe_ci_sa, ymax = pe_mean_sa + pe_ci_sa), width = 0.3, color = "black", position=position_dodge(width = 0.9)) +
  labs(x = "Condition", y = "Accuracy (%)", fill = "Status") +
  ylim(0, 100) +
  theme_minimal() +
  theme(
    plot.margin = unit(c(0.2, 0.2, 0.2, 0.2), "inches"),
    axis.title.x = element_text(face = "bold", size = 13, margin = margin(t = 15)),
    axis.title.y = element_text(face = "bold", size = 13, margin = margin(r = 15)),
    axis.text = element_text(size = 11),
    panel.grid = element_blank(),  # 取消所有格線
    axis.line = element_line(color = "black", size = 0.5),  # 顯示 y 軸和 x 軸線
    axis.ticks = element_line(color = "black", size = 0.5),  # 顯示刻度線
    axis.ticks.length = unit(0.2, "cm")  # 設定刻度線的長度
  )

sapecom_plot


# ggsave(sapecom_plot,
#       filename = "/Users/edwina/Desktop/ResearchOfEdwina/Codes/Quantitative/RPlots/Accuracy/Strict/Strict Accuracy In Post-Exposure Comparison.pdf",
#        device = "pdf" )


```


## PE Tolerant One-Way

```{r}
PE_Tolerant_OneWay_MEM <- lmer(Value ~ Type + (1|ParticipantId), data = PE_Tolerant)
anova(PE_Tolerant_OneWay_MEM)

# Post-Hoc
PE_Tolerant_One_Way_pairwise <- pairs(emmeans(PE_Tolerant_OneWay_MEM, ~ Type))
print(PE_Tolerant_One_Way_pairwise)

PE_Tolerant_One_Way_summary_pairwise <- summary(PE_Tolerant_One_Way_pairwise)
# str(summary_pairwise)
# print(summary_pairwise$p.value)

PE_Tolerant_One_Way_significant_contrasts <- PE_Tolerant_One_Way_summary_pairwise$contrast[PE_Tolerant_One_Way_summary_pairwise$p.value <= 0.05]

PE_Tolerant_One_Way_significant_df <- PE_Tolerant_One_Way_summary_pairwise$df[PE_Tolerant_One_Way_summary_pairwise$p.value <= 0.05]

PE_Tolerant_One_Way_significant_tratio <- PE_Tolerant_One_Way_summary_pairwise$t.ratio[PE_Tolerant_One_Way_summary_pairwise$p.value <= 0.05]

PE_Tolerant_One_Way_significant_p_values <- PE_Tolerant_One_Way_summary_pairwise$p.value[PE_Tolerant_One_Way_summary_pairwise$p.value <= 0.05]
PE_Tolerant_One_Way_significant_p_values <- round(PE_Tolerant_One_Way_significant_p_values, 3)

PE_Tolerant_One_Way_significant_results <- data.frame(contrast = PE_Tolerant_One_Way_significant_contrasts, df = PE_Tolerant_One_Way_significant_df, t.ratio = PE_Tolerant_One_Way_significant_tratio, p.value = PE_Tolerant_One_Way_significant_p_values)

print(PE_Tolerant_One_Way_significant_results)
```


```{r}
PE_Tolerant <- PE_Tolerant %>%
  mutate(
    Type = case_when(
      Type == "PECreTolerantRate" ~ "1st",
      Type == "PECre_Post-ExposureTolerantRate" ~ "2nd",
      Type == "PEConTolerantRate" ~ "1st",
      Type == "PECon_Post-ExposureTolerantRate" ~ "2nd",
      Type == "PEMTolerantRate" ~ "1st",
      Type == "PEM_Post-ExposureTolerantRate" ~ "2nd",
      TRUE ~ Type  # Keep the original value for any unmatched cases
    )
)


pe_taall_stats <- PE_Tolerant %>%
  group_by(Type, Condition) %>%
  summarize(
    pe_mean_ta = round(mean(Value*100), 2),
    pe_sd_ta = round(sd(Value*100), 2),
    n = n(),
    pe_se_ta = pe_sd_ta / sqrt(n) ,  # Standard Error
    pe_ci_ta = qt(0.975, df = n - 1) * pe_se_ta  # 95% Confidence Interval
  )
print(pe_taall_stats)

# 繪製圖形
tapecom_plot <- ggplot(data = pe_taall_stats, aes(x = Condition, y = pe_mean_ta, fill = Type)) + 
  scale_fill_brewer(palette="Reds") +
  geom_bar(stat="identity", position=position_dodge(width = 0.9), width = 0.9) +
  geom_errorbar(aes(ymin = pe_mean_ta - pe_ci_ta, ymax = pe_mean_ta + pe_ci_ta), width = 0.3, color = "black", position=position_dodge(width = 0.9)) +
  labs(x = "Condition", y = "Accuracy (%)", fill = "Status") +
  ylim(0, 100) +
  theme_minimal() +
  theme(
    plot.margin = unit(c(0.2, 0.2, 0.2, 0.2), "inches"),
    axis.title.x = element_text(face = "bold", size = 13, margin = margin(t = 15)),
    axis.title.y = element_text(face = "bold", size = 13, margin = margin(r = 15)),
    axis.text = element_text(size = 11),
    panel.grid = element_blank(),  # 取消所有格線
    axis.line = element_line(color = "black", size = 0.5),  # 顯示 y 軸和 x 軸線
    axis.ticks = element_line(color = "black", size = 0.5),  # 顯示刻度線
    axis.ticks.length = unit(0.2, "cm")  # 設定刻度線的長度
  )

tapecom_plot


# ggsave(sapecom_plot,
#       filename = "/Users/edwina/Desktop/ResearchOfEdwina/Codes/Quantitative/RPlots/Accuracy/Tolerant/Tolerant Accuracy In Post-Exposure Comparison.pdf",
#        device = "pdf" )


```



