---
title: "R Notebook"
output: html_notebook
---

```{r}
library(readr)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(tidyr)
library(gplots)
library(lmerTest)
library(emmeans)
library(RankAggreg)
library(pmr)
```


```{r}
Ranking1 <- read_csv("../Data/MeasurementsFiltered/Ranking1.csv")
Ranking1 <- subset(Ranking1, select = -c(Ranking1ParticipantId))

Ranking2 <- read_csv("../Data/MeasurementsFiltered/Ranking2.csv")
Ranking2 <- subset(Ranking2, select = -c(Ranking2ParticipantId))

Ranking3 <- read_csv("../Data/MeasurementsFiltered/Ranking3.csv")
Ranking3 <- subset(Ranking3, select = -c(Ranking3ParticipantId))

print(Ranking1)
print(Ranking2)
print(Ranking3)
```
## R1 : Descriptive Statistics of Ranking Data
- the test statistics on mean rank: (3+1)/2 = 2
- X^2 distribution with degrees of freedom on mean rank: t-1 -> 3-1 = 2
- p-value = 0.4093654 -> The ranking is uniform! (因為沒有顯著差異)

```{r}
# Transform the individual ranking data to an aggregated format
Ranking1_agg <- rankagg(Ranking1)
print(Ranking1_agg)
cat("\n")

r1 <- destat(Ranking1_agg)
print(r1)

# 套用uniform Mean Rank公式
mean <- rep(2,3)
# print(mean)
chi <- 12*28*sum((r1$mean.rank - mean)^2)/(3*4)

r1_mr_order <- order(r1$mean.rank)
# cat("$mean.rank order: ", r1_mr_order, "\n")

cat("χ^2 test statistic: ", chi, "\n")
cat("p-value: ", dchisq(chi,2), "\n")
```


## R2 : Descriptive Statistics of Ranking Data
- the test statistics on mean rank: (2+1)/2 = 1.5
- X^2 distribution with degrees of freedom on mean rank: t-1 -> 2-1 = 1
- p-value = 0.8071711 -> The ranking is uniform! (因為沒有顯著差異)

```{r}
# Transform the individual ranking data to an aggregated format
Ranking2_agg <- rankagg(Ranking2)
print(Ranking2_agg)

r2 <- destat(Ranking2_agg)
print(r2)

# 套用uniform Mean Rank公式
mean <- rep(1.5,2)
# print(mean)
chi <- 12*28*sum((r2$mean.rank - mean)^2)/(2*3)

r2_mr_order <- order(r2$mean.rank)
# cat("$mean.rank order: ", r2_mr_order, "\n")

cat("χ^2 test statistic: ", chi, "\n")
cat("p-value: ", dchisq(chi,1), "\n")
cat("\n")
```


## R3 : Descriptive Statistics of Ranking Data
- the test statistics on mean rank: (7+1)/2 = 4
- X^2 distribution with degrees of freedom on mean rank: t-1 -> 7-1 = 6
- p-value = 0.09064667 -> The ranking is uniform! (因為沒有顯著差異)

```{r}
# Transform the individual ranking data to an aggregated format
Ranking3_agg <- rankagg(Ranking3)
print(Ranking3_agg)

r3 <- destat(Ranking3_agg)
print(r3)

# 套用uniform Mean Rank公式
mean <- rep(4,7)
# print(mean)
chi <- 12*28*sum((r3$mean.rank - mean)^2)/(7*8)


cat("χ^2 test statistic: ", chi, "\n")
cat("p-value: ", dchisq(chi,6), "\n")
cat("\n")
```

