---
title: "R Notebook"
output: html_notebook
---

```{r}
library(readr)
library(tidyverse)
library(ggplot2)
library(dplyr)
library(tidyr)
library(gplots)
library(ggpubr)
library(emmeans)
library(lmerTest)
```

```{r}
Response_Time <- read_csv("../Data/MeasurementsFiltered/Response_ReactionTime.csv")
# view(Response_Time)
print(Response_Time)

# 只取PE中第二次的時間
PE_Second <- Response_Time[!(Response_Time$Status %in% c("PEM", "PECon", "PECre")), ]
print(PE_Second)

# 只有PE的所有狀態
PE_filtered_data <- Response_Time %>% filter(grepl("PE", Condition))
print(PE_filtered_data)
```

## Sumarry & Standards derivation (PE只取第二次的)

```{r}
summary(PE_Second) #看各列的資料(Min, 1st Qu, Median, Mean, 3rd Qu, Max)

cat("\n")
cat("Standard Derivation of Response Time = ",sd(PE_Second$ReactionTime))
```


### PlotMeans (PE狀態只取第二次的秒數)

```{r}
# Reorder the levels of the "Condition" factor so that "Control" comes first
PE_Second <- PE_Second %>%
  mutate(Condition = factor(Condition, levels = c("Control", "CCTCon", "CCTCre", "CCTM", "PECon", "PECre", "PEM")))

plotmeans(PE_Second$ReactionTime ~ PE_Second$Condition,
          main = "Reaction Time of All Conditions",
          xlab = "Condition",
          ylab = "Reaction Time (s)",
          ylim = c(5, 8),
          n.label = FALSE,
          connect = FALSE)


# Summary statistics
rtall_stats <- PE_Second %>%
  group_by(Condition, Placement, LabelType) %>%
  summarize(
    mean_reaction_time = mean(ReactionTime),
    sd_reaction_time = sd(ReactionTime),
    n = n(),  # Sample size for each group
    se_reaction_time = sd_reaction_time / sqrt(n),  # Standard Error
    ci_reaction_time = qt(0.975, df = n - 1) * se_reaction_time  # 95% Confidence Interval
  )
print(rtall_stats)

# Define custom colors for each combination of Placement and LabelType
custom_colors <- c(
  "Control" = "#fa75a2",
  "CCTCon" = "#a6cee3",  # light blue
  "CCTCre" = "#1f78b4",  # medium blue
  "CCTM" = "#2e4194",  # dark blue
  "PECon" = "#b2df8a",  # light green
  "PECre" = "#33a02c",  # medium green
  "PEM" = "#006400"  # dark green
)

# Modify the plot to use confidence intervals instead of standard deviation
rtall <- ggplot(data = rtall_stats, aes(x = Condition, y = mean_reaction_time, fill = Condition)) + 
  scale_fill_manual(values = custom_colors) +
  geom_col(width = 0.6) +
  geom_errorbar(data = rtall_stats, 
                aes(x = Condition, ymin = mean_reaction_time - ci_reaction_time, ymax = mean_reaction_time + ci_reaction_time), width = 0.3, color = "black") +
  labs(x = "Condition", y = "Reaction Time (s)") +
  theme_minimal() +
  theme(
    plot.margin = unit(c(0.2, 0.2, 0.2, 0.2), "inches"),
    axis.title.x = element_text(face = "bold", size = 13, margin = margin(t = 15)),
    axis.title.y = element_text(face = "bold", size = 13, margin = margin(r = 15)),
    axis.text = element_text(size = 11),
    panel.grid = element_blank(),  # Remove grid lines
    axis.line = element_line(color = "black", size = 0.5),  # Show axis lines
    axis.ticks = element_line(color = "black", size = 0.5),  # Show tick lines
    axis.ticks.length = unit(0.2, "cm")  # Set tick length
  ) +
  guides(fill = FALSE)  # Remove the legend for the fill

rtall

# ggsave(rtall, 
#       filename = "/Users/edwina/Desktop/ResearchOfEdwina/Codes/Quantitative/RPlots/ReactionTime/Reaction Time of All Conditions.pdf",
#        device = "pdf" )


```


## Two-Way ANOVA (PE Second Time)
- Mixed Effects Models

```{r}
Exclude_Control_PE_Second <- PE_Second %>% 
  filter(!(LabelType == "Control" & Placement == "Control"))
Exclude_Control_PE_Second
table(Exclude_Control_PE_Second$LabelType, Exclude_Control_PE_Second$Placement)

# Fit the linear mixed-effects models
RT_TwoWay_MEM <- lmer(ReactionTime ~ LabelType * Placement + (1|ParticipantId), data = Exclude_Control_PE_Second)

# Perform ANOVA
anova(RT_TwoWay_MEM)

# Post-Hoc
RT_TwoWay_pairwise <- pairs(emmeans(RT_TwoWay_MEM, ~ LabelType * Placement))
print(RT_TwoWay_pairwise)

RT_TwoWay_summary_pairwise <- summary(RT_TwoWay_pairwise)
# str(summary_pairwise)
#print(summary_pairwise$p.value)

significant_contrasts <- RT_TwoWay_summary_pairwise$contrast[RT_TwoWay_summary_pairwise$p.value <= 0.05]

significant_df <- RT_TwoWay_summary_pairwise$df[RT_TwoWay_summary_pairwise$p.value <= 0.05]

significant_tratio <- RT_TwoWay_summary_pairwise$t.ratio[RT_TwoWay_summary_pairwise$p.value <= 0.05]

significant_p_values <- RT_TwoWay_summary_pairwise$p.value[RT_TwoWay_summary_pairwise$p.value <= 0.05]
significant_p_values <- round(significant_p_values, 3)

significant_results <- data.frame(contrast = significant_contrasts, df = significant_df, t.ratio = significant_tratio, p.value = significant_p_values)

print(significant_results)
```



## Plotmeans
```{r}
plotmeans(PE_Second$ReactionTime ~ PE_Second$LabelType,
          main = "Reaction Time in Different Label Types",
          xlab = "Label Type",
          ylab = "Reaction Time (s)",
          ylim = c(5,8),
          n.label = FALSE,
          connect = FALSE)  


plotmeans(PE_Second$ReactionTime ~ PE_Second$Placement,
          main = "Reaction Time in Different Placements",
          xlab = "Placement",
          ylab = "Reaction Time (s)",
          ylim = c(5,7),
          n.label = FALSE,
          connect = FALSE)  
```


## Interaction of Label Type and Placement

```{r}
# Label Type
labeltype_comparisons <- pairs(emmeans(RT_TwoWay_MEM, "LabelType"))
summary(labeltype_comparisons)

label_stats <- Exclude_Control_PE_Second %>%
  group_by(LabelType) %>%
  summarize(
    lt_mean_reaction_time = round(mean(ReactionTime), 2),
    lt_sd_reaction_time = round(sd(ReactionTime), 2),
    n = n(),  # Sample size for each group
    lt_se_reaction_time = lt_sd_reaction_time / sqrt(n),  # Standard Error
    lt_ci_reaction_time = qt(0.975, df = n - 1) * lt_se_reaction_time  # 95% Confidence Interval
  )
print(label_stats)

# Plot the boxplot with error bars
rt_lt <- ggplot(data = label_stats, aes(x = LabelType, y = lt_mean_reaction_time, fill = LabelType)) + 
  scale_fill_brewer(palette="Greys") +
  geom_col(width = 0.6) +
  geom_errorbar(aes(x = LabelType, ymin = lt_mean_reaction_time - lt_ci_reaction_time, ymax =  lt_mean_reaction_time + lt_ci_reaction_time), width = 0.2, color = "black") +
  labs(x = "(A) Label Type", y = "Reaction Time (s)") +
  ylim(0, 10) +
  theme_minimal() +
  theme(
    axis.title.x = element_text(face = "bold", size = 13, margin = margin(t = 15)),
    axis.title.y = element_text(face = "bold", size = 13, margin = margin(r = 15)),
    axis.text = element_text(size = 11),
    axis.text.x = element_text(angle=45, vjust=1, hjust=1),
    panel.grid = element_blank(),  # 取消所有格線
    axis.line = element_line(color = "black", size = 0.5),  # 顯示 y 軸和 x 軸線
    axis.ticks = element_line(color = "black", size = 0.5),  # 顯示刻度線
    axis.ticks.length = unit(0.2, "cm")  # 設定刻度線的長度
  ) +
  guides(fill = FALSE)  # Remove the legend for the fill

rt_lt


# Placement
pairs(emmeans(RT_TwoWay_MEM, "Placement"))

placement_stats <- Exclude_Control_PE_Second %>%
  group_by(Placement) %>%
  summarize(
    pt_mean_reaction_time = round(mean(ReactionTime), 2),
    pt_sd_reaction_time = round(sd(ReactionTime), 2),
    n = n(),  # Sample size for each group
    pt_se_reaction_time = pt_sd_reaction_time / sqrt(n),  # Standard Error
    pt_ci_reaction_time = qt(0.975, df = n - 1) * pt_se_reaction_time  # 95% Confidence Interval
  )
print(placement_stats)

# Plot the boxplot with error bars
rt_pt <- ggplot(data = placement_stats, aes(x = Placement, y = pt_mean_reaction_time, fill = Placement)) + 
  scale_fill_manual(values = c("Concurrent" = "#1f78b4",
                               "Post-Exposure" = "#33a02c")) + 
  geom_col(width = 0.4) +  # Set the bar color here
  geom_errorbar(data = placement_stats, aes(x = Placement, ymin = pt_mean_reaction_time - pt_ci_reaction_time, ymax = pt_mean_reaction_time + pt_ci_reaction_time), width = 0.2, color = "black") +
  labs(x = "(B) Placement") +
  theme_minimal() +
  theme(
    axis.title.x = element_text(face = "bold", size = 13, margin = margin(t = 15)),
    axis.title.y = element_blank(),  # 取消顯示 y 軸名稱
    axis.text = element_text(size = 11),
    axis.text.x = element_text(angle=45, vjust=1, hjust=1),
    panel.grid = element_blank(),  # 取消所有格線
    axis.line = element_line(color = "black", size = 0.5),  # 顯示 y 軸和 x 軸線
    axis.ticks = element_line(color = "black", size = 0.5),  # 顯示刻度線
    axis.ticks.length = unit(0.2, "cm")  # 設定刻度線的長度
  ) +
  guides(fill = FALSE)  # Remove the legend for the fill

  
rt_fig <- ggarrange(
  rt_lt, rt_pt,
  ncol = 2, nrow = 1,
  align = "h"  # 垂直對齊
)
rt_fig + theme(plot.margin = unit(c(0.3, 0.2, 0.1, 0.2), "inches"))

# ggsave(rt_fig, 
#       filename = "/Users/edwina/Desktop/ResearchOfEdwina/Codes/Quantitative/RPlots/ReactionTime/Reaction Time of Lable Type and Placement.pdf",
#        device = "pdf" )

```



```{r}
RT_MC <- PE_Second %>% filter(grepl("Mix", LabelType) & grepl("Concurrent", Placement))
summary(RT_MC)
sd(RT_MC$ReactionTime)
```

## One-Way ANOVA (Include Control, PE Second Time): F(6,270) = 4.9, 8.954e-05
- Mixed Effects Models
- Report ANOVA result: `F(num df, denom df)=F Value, p-value`

```{r}
# Fit the mixed-effects model
RT_OneWay_MEM <- lmer(ReactionTime ~ Condition + (1|ParticipantId), data = PE_Second)
anova(RT_OneWay_MEM)


# Post-Hoc
RT_OneWay_pairwise <- pairs(emmeans(RT_OneWay_MEM, ~ Condition))
print(RT_OneWay_pairwise)

RT_OneWay_summary_pairwise <- summary(RT_OneWay_pairwise)
# str(summary_pairwise)
# print(summary_pairwise$p.value)

RT_OneWay_significant_contrasts <- RT_OneWay_summary_pairwise$contrast[RT_OneWay_summary_pairwise$p.value <= 0.05]

RT_OneWay_significant_df <- RT_OneWay_summary_pairwise$df[RT_OneWay_summary_pairwise$p.value <= 0.05]

RT_OneWay_significant_tratio <- RT_OneWay_summary_pairwise$t.ratio[RT_OneWay_summary_pairwise$p.value <= 0.05]

RT_OneWay_significant_p_values <- RT_OneWay_summary_pairwise$p.value[RT_OneWay_summary_pairwise$p.value <= 0.05]
RT_OneWay_significant_p_values <- round(RT_OneWay_significant_p_values, 3)

RT_OneWay_significant_results <- data.frame(contrast = RT_OneWay_significant_contrasts, df = RT_OneWay_significant_df, t.ratio = RT_OneWay_significant_tratio, p.value = RT_OneWay_significant_p_values)

print(RT_OneWay_significant_results)
```

### PlotMeans (Post-Exposure 組間)

```{r}
PE_filtered_data <- PE_filtered_data %>%
  mutate(
    Status = case_when(
      Status %in% c("PECre", "PECon", "PEM") ~ "1st",
      Status %in% c("PECre_Post-Exposure", "PECon_Post-Exposure", "PEM_Post-Exposure") ~ "2nd",
      TRUE ~ as.character(Status)  # 如果有其他狀況，保留原狀態
    ))

rtpecom_stats <- PE_filtered_data %>%
  group_by(Status, Condition) %>%
  summarize(
    pe_mean_reaction_time = round(mean(ReactionTime), 2),
    pe_sd_reaction_time = round(sd(ReactionTime), 2),
    n = n(),  # Sample size for each group
    pe_se_reaction_time = pe_sd_reaction_time / sqrt(n),  # Standard Error
    pe_ci_reaction_time = qt(0.975, df = n - 1) * pe_se_reaction_time  # 95% Confidence Interval
  )
print(rtpecom_stats)

# 繪製圖形
rtpecom_plot <- ggplot(data = rtpecom_stats, aes(x = Condition, y = pe_mean_reaction_time, fill = Status)) + 
  scale_fill_brewer(palette="Reds") +
  geom_bar(stat="identity", position=position_dodge(width = 0.9), width = 0.9) +
  geom_errorbar(aes(ymin = pe_mean_reaction_time - pe_ci_reaction_time, ymax = pe_mean_reaction_time + pe_ci_reaction_time), width = 0.3, color = "black", position=position_dodge(width = 0.9)) +
  labs(x = "Condition", y = "Reaction Time (s)") +
  ylim(0, 10) +
  theme_minimal() +
  theme(
    plot.margin = unit(c(0.2, 0.2, 0.2, 0.2), "inches"),
    axis.title.x = element_text(face = "bold", size = 13, margin = margin(t = 15)),
    axis.title.y = element_text(face = "bold", size = 13, margin = margin(r = 15)),
    axis.text = element_text(size = 11),
    panel.grid = element_blank(),  # 取消所有格線
    axis.line = element_line(color = "black", size = 0.5),  # 顯示 y 軸和 x 軸線
    axis.ticks = element_line(color = "black", size = 0.5),  # 顯示刻度線
    axis.ticks.length = unit(0.2, "cm")  # 設定刻度線的長度
  )

rtpecom_plot

# ggsave(rtpecom_plot,
#       filename = "/Users/edwina/Desktop/ResearchOfEdwina/Codes/Quantitative/RPlots/ReactionTime/Reaction Time In Post-Exposure Comparison.pdf",
#        device = "pdf" )

```


## One-Way ANOVA (Post-Exposure 組間): F(5,231) = 2.4203, 0.03659
- Mixed Effects Models
- Report ANOVA result: `F(num df, denom df)=F Value, p-value`

```{r}
RT_PE_OneWay_MEM <- lmer(ReactionTime ~ Status + (1|ParticipantId), data = PE_filtered_data)
anova(RT_PE_OneWay_MEM)

# Post-Hoc
RT_PE_pairwise <- pairs(emmeans(RT_PE_OneWay_MEM, ~ Status))
print(RT_PE_pairwise)

RT_PE_summary_pairwise <- summary(RT_PE_pairwise)
# str(summary_pairwise)
# print(summary_pairwise$p.value)

RT_PE_significant_contrasts <- RT_PE_summary_pairwise$contrast[RT_PE_summary_pairwise$p.value <= 0.05]

RT_PE_significant_df <- RT_PE_summary_pairwise$df[RT_PE_summary_pairwise$p.value <= 0.05]

RT_PE_significant_tratio <- RT_PE_summary_pairwise$t.ratio[RT_PE_summary_pairwise$p.value <= 0.05]

RT_PE_significant_p_values <- RT_PE_summary_pairwise$p.value[RT_PE_summary_pairwise$p.value <= 0.05]
RT_PE_significant_p_values <- round(RT_PE_significant_p_values, 3)

RT_PE_significant_results <- data.frame(contrast = RT_PE_significant_contrasts, df = RT_PE_significant_df, t.ratio = RT_PE_significant_tratio, p.value = RT_PE_significant_p_values)

print(RT_PE_significant_results)
```
